Discovery of barium stars in the LAMOST survey

### 2018-01-22 article/ms.tex
add comments etc

\section{Methods} \label{sec:methods}
\subsection{LAMOST Analysis}
\subsubsection{Data-driven Analysis}
The spectral data of our stars were obtained from the \textit{Cannon} fits predictive model implemented by \citet{ho2017} on the LAMOST (Large Sky Area Multi-Object Fibre Spectroscopic Telescope) DR2 release \citep{luo2015}. The LAMOST spectral resolving power of R = 1800, a wavelength coverage from 3700\AA\ to 9000\AA, and \todo{a nominal S/N ratio of 100 (is this true?)}\countertodo{I read it in a paper somewhere, is it not true ?}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must exceed A$\leq$-0.05.
\item Both amplittudes must be measured within 3$\sigma$ $(|A|/\sigma _A \geq 3)$.
\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}$(\lambda \leq 2)$.
\item $\chi^2 \leq 3$.
\item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$.
\end{enumerate}
In addition, a visual observation of the accuracy between each normalised LAMOST flux and its accompanying data driven model was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated the 257 Barium star candidates as listed in Table \ref{table:table1}.

@@

\subsection{MAGELLAN Analysis}

\subsubsection{Observations}

\subsubsection{Abundance Analysis}

\subsubsection{Abundance Uncertainties}

\subsection{Dynamics}
The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, producing 21 matches, and then using gala Python package to intergrate the galactic dynamics. The Milky Way potential model was used to integrate the orbits of our candidates back a \todo{number} years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.

>>>>

\section{Methods} \label{sec:methods}
\subsection{LAMOST Analysis}
\subsubsection{Data-driven Analysis}
The LAMOST (Large sky Area Multi-Object Fibre Spectrographic) survey released low-resolution ($\mathcal{R} \approx 1800$) optical spectra (3700\,\AA\ to 9000\,\AA) for over two million stars in their second data release \citep{luo2015}. Stellar parameters ($T_{\rm eff}$, $\log{g}$, [M/H], [$\alpha$/M]) were derived using a data-driven model constructed using high fidelity APOGEE labels of 9,952 stars in common between LAMOST and the APOGEE survey. \todo{Write more about this: the precision in parameters, how giants were selected from dwarfs, and then talk about how many giant spectra we used}.

@@

\begin{enumerate} 
\item Profile amplitude for both enhancement lines must exceed A$\leq$-0.05.
\item Both amplittudes must be measured within 3$\sigma$ $(|A|/\sigma _A \geq 3)$.
\item The wavelength at each absorption line must be within $2$\AA \hspace{0.2mm}$(\lambda \leq 2)$.
\item $\chi^2 \leq 3$.
\item And, the spectra must have a signal-to-noise ratio of S/N $\geq 30$ per pixel.
\end{enumerate}
In addition, a visual observation of the accuracy between each normalised LAMOST flux and its accompanying data driven model was undertaken to exclude any results containing, false positives, candidates exhibiting data reduction issues, apparent absorption finer then the spectral resolution, and overly noisy normalised LAMOST spectra. This combined method generated the 257 Barium star candidates as listed in Table \ref{table:table1}.

@@

\subsection{Follow-up observations with Magellan/MIKE}

\subsubsection{Observations}
On the night of \todo{X} January 2018 we performed follow-up observations of \todo{X} barium star candidates using the MIKE spectrograph on the Magellan Clay telescope at Las Campanas Observatory, Chile. Candidates for follow-up observations were chosen based on observability constraints and ranked by their apparent visual magnitude. We observed \todo{X} stars in good seeing using the 0.7 arcsecond slit and 2x2 spatial on-chip binning, which provides a spectral resolution of ($\mathcal{R} \approx \todo{22,000}$). Exposure times were set to achieve a S/N ratio of 30 per pixel at 4500\,\AA. We acquired calibration (biases, milky, quartz, and Th-Ar arc lamp) frames in the afternoon.

We reduced the data using the \texttt{CarPy} Python package \citep{kels03,kels14}. We used spline functions to continuum-normalise individual echelle orders, and resampled the normalised spectra onto a uniform-sized wavelength map. We used a rest-frame normalised template of a FGK-type star to place the observed spectra in the rest frame.

\subsubsection{Abundance Analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{Ho_2017}. Following the procedure outlined in \citep{Casey_2014}, we measured the strength of atomic absorption lines by fitting Gaussian profiles to the continuum-normalised spectra. Most elemental abundances were derived directly from these line measurements, except for elements that show significant hyperfine splitting \todo{(e.g., )} or blending \todo{(e.g., X)}. In these situations, we adopted a spectral synthesis approach. \todo{citations for line lists}

\todo{Some sentences for andy to add regarding abundance analysis and verification of stellar parameters from LAMOST}

\todo{Were ant of the stars observed with Magellan/MIKE the stars enhanced in Na? C?}

%\subsubsection{Abundance Uncertainties}

\subsection{Dynamics}
\todo{rewrite this with more detail: see Casey \& Schlaufman (2017) to see how much detail you should give for dynamics analysis...}
The dynamical analysis of our barium star candidates was accomplished by crossing matching the sample with GAIA \todo{ref gaia}, producing 21 matches, and then using gala Python package to intergrate the galactic dynamics. The Milky Way potential model was used to integrate the orbits of our candidates back a \todo{number} years, and compute distributions of orbital properties including orbital period, orbital energy, apocenter, eccentricity, and angular momentum in z.
